A novel distributed nature-inspired algorithm for solving optimization problems\thanks{Supported by organization x.}

### 2021-08-16 paper.tex
Paper update
Work in progress

As a proof-of-concept, we implemented the algorithm with Docker containers by
solving the OneMax problem comparing it with a basic (sequential) GA algorithm,
where it showed favorable and promising results.

>>>>

As a proof-of-concept, we implemented the algorithm with Docker containers by
solving the OneMax problem to compare it with a traditional (sequential) GA
algorithm using the DEAP library. The OneMax problem uses a genetic algorithm
to evolve a population of randomly generated individuals with zeros and ones,
and it stops until a solution of only ones is found.

In this experiment, we needed to match or balance the experimentation
parameters according to the specifications of the algorithm used by the DEAP
library. This is to be able to verify if our algorithm would also converge on
the solutions in a similar number of evaluations and execution time.

\section{Results}

In our experiments, we found that for simple problems, the cost of
communication between containers will increase the total time of execution,
however, we believe that the opposite must also be true: for complex problems,
distributing the work on multiple resources must reduce time, making the
communication cost negligible.

This scheme allows for multiple parameter's fine tunning, granting us the
freedom to experiment with different selection and reproduction strategies
simultaneously, which will impact how fast it finds the solution and the
obtained quality.

\section{Conclusions}

In this research, we were able to demonstrate that it is possible to evolve a
population of individuals, similar to a Genetic Algorithm (GA), using a
distributed, parallel, and asynchronous methodology.

We implemented the algorithm with Docker containers by solving the OneMax
problem comparing it with a traditional (sequential) GA algorithm, where it
showed favorable and promising results. To further validate this work we could
use control or something more complex and demanding problem that requires to
compute real numbers.
